Summary of PM2.5 Nonattainment  Analysis

### 2020-11-20 Analysis Files/Paper_Analysis_317_pr_v1.Rmd
adding Prathyusha's code

---
title: "Summary of PM2.5 Nonattainment  Analysis"
author: "Cory Zigler"
date: "December 20, 2016"
output: pdf_document
---

```{r}
rm(list=ls())
set.seed(51)
# library(HEIfunctions)
source("mvspmod.R")
library(maps)
library(PSAgraphics)
library(data.table)
library(randomForest)

source('mybalcheck.R')
source('ReadSimsFunction.R')
getrate=function(vec, denom){
  return(vec*1000/denom)
}

@@

whichyears = 1999:2012  ## only 3 monitors in 1997, only 4 in 1998
whichvar = "Arithmetic.Mean" ##"X95th.Percentile" ##Arithmetic.Mean"
attaindat=read.csv('Data Construction/Other Data Files/EPA Nonattainment Table.csv')
attaindat$FIPS=paste(formatC(attaindat$fips_state, width=2, flag="0"), formatC(attaindat$fips_cnty, width=3, flag="0"), sep="")
attaindat = subset(attaindat, pollutant=='PM-2.5 1997')
attaindat$a_2012 = ifelse(attaindat$pw_2012 %in% c("P", "W"), 1, 0)
checka_2012 = attaindat[, c("FIPS", "a_2012")]
check_attain_fu = merge(dat, checka_2012, by = "FIPS", all.x = TRUE)
check_attain_fu$a_2012[is.na(check_attain_fu$a_2012)] = 0
with(check_attain_fu, table(a, a_2012))
print(paste("Percentage of 2005 nonattainment areas that remained in nonattainment in 2012 =", with(check_attain_fu, round(sum(a_2012==1)/(sum(a==1)),2))))
```

@@

# dat$ps = get_propensity_scores()
dat$ps = get_propensity_scores(method=method)

mina1 = min(dat$ps[dat$a==1])
maxa0 = max(dat$ps[dat$a==0])
dat$outofrange = 0

@@

@@

# NEW: Stratified DIM estimate (SASKIA) without adjusting for covariates
```{r}
### Medium Models
# load('vars_with_imbalance.RData')
# vars_with_imbalance
# toadjust = vars_with_imbalance[!(vars_with_imbalance %in% c("pmbase", "Tot_den_for_death_MA_FFS.2012"))]
# medformula = as.formula(paste("y ~", paste(c("pscat", "pmbase2002_2004", toadjust), collapse = "+")))
# my = glm(medformula, data = dat)
# formula = my$formula
strata <- unique(dat$pscat[dat$outofrange == 0])
dat_prune <- dat[dat$outofrange == 0]
# stratified DIM estimate
stratum_tau <- numeric(length(strata))
stratum_weight <- numeric(length(strata))
stratum_var <- numeric(length(strata))
stratum_treat_count <- numeric(length(strata))
stratum_cont_count <- numeric(length(strata))
# Compute within-stratum DIM (tau) and variance estimates
for (i in 1:length(strata)){
  ## Tau (average causal effect of treated vs. control) ##
  # j <- adynarski$prop >= strata[i] & adynarski$prop <= strata[i+1]
  j <- (dat_prune$pscat == strata[i])
  treated <- dat_prune$a == 1
  control <- dat_prune$a == 0
  strat_treat <- dat_prune$pmfu[j & treated]
  strat_treat <- strat_treat[!is.na(strat_treat)]
  strat_control <- dat$pmfu[j & control]
  strat_control <- strat_control[!is.na(strat_control)]
  y_1 <- sum(strat_treat, na.rm = TRUE) # effect among treated units in strata
  N_1 <- length(strat_treat) # number of treated units in strata
  y_0 <- sum(strat_control, na.rm = TRUE) # effect among control units in strata
  N_0 <- length(strat_control) # number of control units in strata 
  stratum_tau[i] <- (1/N_1)*y_1 - (1/N_0)*y_0
  stratum_weight[i] <- (N_1+N_0)/nrow(dat_prune)
  stratum_treat_count[i] <- N_1
  stratum_cont_count[i] <- N_0
  ## Variance (Conservative Estimator)
  v_1 <- sum((strat_treat- ((1/N_1)*y_1))^2)/(N_1-1) 
  v_0 <- sum((strat_control- ((1/N_0)*y_0))^2)/(N_0-1) 
  stratum_var[i] <- v_1/N_1 + v_0/N_0
}

# weight within stratum DIm and variance estimates to get overall estimate
stratified_dim <- sum(stratum_tau * stratum_weight)
print(paste("Stratified DIM estimate of ATE =", round(stratified_dim, 5)))
stratified_var <- sum(stratum_var * stratum_weight^2)
print(paste("Estimate of variance =", round(stratified_var, 5)))

## 95% CI based on Normal Approximation##
ci_lower <- stratified_dim + qnorm(.05/2)*sqrt(stratified_var)
ci_upper <- stratified_dim + qnorm(1-(.05/2))*sqrt(stratified_var)
print(paste("95% CI interval: (", round(ci_lower, 5), ",", round(ci_upper, 5), ")"))
stratum_treat_count
stratum_cont_count
```

>>>>

---
title: "Summary of PM2.5 Nonattainment  Analysis"
author: "Cory Zigler"
date: "December 20, 2016"
output:
  pdf_document: default
  word_document: default
---

```{r}
setwd("~/Desktop/MSE_327/Project")
rm(list=ls())
set.seed(51)
# library(HEIfunctions)
#source("mvspmod.R")
library(maps)
library(PSAgraphics)
library(data.table)
library(randomForest)

source('mybalcheck.R')
#source('ReadSimsFunction.R')
getrate=function(vec, denom){
  return(vec*1000/denom)
}

@@

whichyears = 1999:2012  ## only 3 monitors in 1997, only 4 in 1998
whichvar = "Arithmetic.Mean" ##"X95th.Percentile" ##Arithmetic.Mean"
# attaindat=read.csv('Data Construction/Other Data Files/EPA Nonattainment Table.csv')
# attaindat$FIPS=paste(formatC(attaindat$fips_state, width=2, flag="0"), formatC(attaindat$fips_cnty, width=3, flag="0"), sep="")
# attaindat = subset(attaindat, pollutant=='PM-2.5 1997')
# attaindat$a_2012 = ifelse(attaindat$pw_2012 %in% c("P", "W"), 1, 0)
# checka_2012 = attaindat[, c("FIPS", "a_2012")]
# check_attain_fu = merge(dat, checka_2012, by = "FIPS", all.x = TRUE)
# check_attain_fu$a_2012[is.na(check_attain_fu$a_2012)] = 0
# with(check_attain_fu, table(a, a_2012))
# print(paste("Percentage of 2005 nonattainment areas that remained in nonattainment in 2012 =", with(check_attain_fu, round(sum(a_2012==1)/(sum(a==1)),2))))
```

@@

# dat$ps = get_propensity_scores()
dat$ps = get_propensity_scores(method=method)
dat$psrf = get_propensity_scores(method= "RF")

mina1 = min(dat$ps[dat$a==1])
maxa0 = max(dat$ps[dat$a==0])
mina1rf = min(dat$psrf[dat$a ==1])
maxa0rf = max(dat$psrf[dat$a==0])

dat$outofrange = 0

@@

## Subclassification and Regression
```{r,  echo=FALSE}
new_dat = dat
dat_m = as.matrix(dat)
colnames_new = c()
for(i in 1:length(vars_with_imbalance))
{
  #print(i)
  ind = which(colnames(dat) == vars_with_imbalance[i])
  #print(ind)
  new_dat[,(2*i-1)] = as.numeric(dat_m[,ind])
  new_dat[,(2*i )] = (dat$a)*(as.numeric(dat_m[,ind]) - mean(new_dat[,(2*i)]))
  colnames_new = c(colnames_new, vars_with_imbalance[i], paste(vars_with_imbalance[i] , "adj", sep = "_"))
}
new_dat = new_dat[, 1:(2*length(vars_with_imbalance))]
#dim(new_dat)
colnames(new_dat) = colnames_new
new_dat$a = dat$a
new_dat$pmfu = dat$pmfu
colnames(new_dat)

lm_model1 <- lm(pmfu ~ ., data = new_dat, na.action = na.omit)
lm_model1$coefficients
new_dat=  as.data.frame(new_dat)
#summary(lm_model1)
effect <-  c(0, dim(new_dat)[1])
#lm_model2 <- lm(inclformula_1, data = dat, na.action = na.omit)
for(i in 1:dim(new_dat)[1])
{
  # cat("i is ", i)
  # cat("\n")
  temp= lm_model1$coefficients[22]
  for(j in 1:10)
  {
    temp = temp + ((lm_model1$coefficients[(2*j + 1)])*new_dat[i, ((2*j) -1)])
  }
  effect[i] = temp
}
#effect
mean(effect)
#summary(lm_model2)
```

```{r,  echo=FALSE}
new_dat = dat
dat_m = as.matrix(dat)
colnames_new = c()
for(i in 1:length(vars_with_imbalance))
{
  #print(i)
  ind = which(colnames(dat) == vars_with_imbalance[i])
  #print(ind)
  new_dat[,i] = as.numeric(dat_m[,ind])
  #new_dat[,(2*i )] = (dat$a)*(as.numeric(dat_m[,ind]) - mean(new_dat[,(2*i)]))
  colnames_new = c(colnames_new, vars_with_imbalance[i])
}
new_dat = new_dat[, 1:(length(vars_with_imbalance))]
#dim(new_dat)
colnames(new_dat) = colnames_new
new_dat$a = dat$a
new_dat$pmfu = dat$pmfu
new_dat=  as.data.frame(new_dat)
lm_model1 <- lm(pmfu ~ ., data = new_dat, na.action = na.omit)
summary(lm_model1)
```
```{r, echo = FALSE}
compute_var <- function(Z, N, y)
{
  y_bar <- sum(Z * y) / N
  var_Z <- 1/(N-1) * sum((Z * (y-y_bar)^2)) 
  return(var_Z)
}
```

## For Logistic
```{r, echo = FALSE}
dat$outofrange[dat$ps>maxa0 & dat$a==1]=1
dat$outofrange[dat$ps<mina1 & dat$a==0]=1

##### Define PS categories ##################
cuts = quantile(dat$ps[dat$outofrange==0], seq(.25, .75, .25)) # quartiles
dat$pscat[dat$outofrange==0] = as.numeric(cut(dat$ps[dat$outofrange==0], breaks=c(0,cuts,1), include.lowest=TRUE))
dat$pscat = as.factor(dat$pscat)
perc_list = cuts

strata_dim <- rep(0,length(perc_list)+1) 
strata_var <- rep(0,length(perc_list)+1) 
strata_weight <- rep(0,length(perc_list)+1)
strata_N1 <- rep(0,length(perc_list)+1) 
strata_N0 <- rep(0,length(perc_list)+1)

strata_dim_after <- rep(0,length(perc_list)+1) 
strata_var_after <- rep(0,length(perc_list)+1) 
strata_weight_after <- rep(0,length(perc_list)+1)

for (i in 1:(length(perc_list)+1))
{
  if (i ==1)
  {
    zst_ind <- which(dat$ps >= 0 & dat$ps <= perc_list[i] & dat$outofrange == 0)
    zst <- dat[dat$ps >= 0 & dat$ps <= perc_list[i] & dat$outofrange == 0, c("a", "pmfu")]
  } 
  else if( i == (length(perc_list)+1) )
  {
    zst_ind <- which(dat$ps >= perc_list[i-1] & dat$ps <= 1 & dat$outofrange == 0)
    zst <- dat[dat$ps >= perc_list[i-1] & dat$ps <= 1 & dat$outofrange == 0, c("a", "pmfu")]
  }
  else
  {
    #print("check")
    zst_ind <- which(dat$ps >= perc_list[i-1] & dat$ps <= perc_list[i] & dat$outofrange == 0)
    zst <- dat[dat$ps >= perc_list[i-1] & dat$ps <= perc_list[i] & dat$outofrange == 0, c("a", "pmfu")]
  }

  na_ind = which(is.na(zst[,"pmfu"]) == FALSE)
  zst = zst[na_ind,]
  N_1 <- sum(zst[,"a"]) 
  strata_N1[i] = N_1
  N_0 <- nrow(zst) - N_1 
  strata_N0[i] = N_0
  Z <- zst[,"a"]
  y <- zst[,"pmfu"]

  # Z = Z[na_ind]
  # y = y[na_ind]

  strata_dim[i] <- (1/N_1 * sum(Z * y) - 1/N_0 * sum((1 - Z) * y))
  V_1 <- compute_var(Z, N_1, y)
  V_0 <- compute_var(1-Z, N_0, y) 
  strata_var[i] <- V_1/N_1 + V_0/N_0
  strata_weight[i] <- nrow(zst)#/nrow(dat)

  lm_sub <- lm(pmfu ~ ., data = new_dat[zst_ind,], na.action = na.omit)
  strata_dim_after[i] <- lm_sub$coefficients[12]
  strata_var_after[i] <- (summary(lm_sub)$coefficients[12,2])^2
  strata_weight_after[i] <- length(zst)/length(which(dat$outofrange == 0))
}
strata_weight = strata_weight/sum(strata_weight)
tau_dim <- sum(strata_dim * strata_weight) 
var_dim <- sum(strata_var * strata_weight)

tau_dim_after <- sum(strata_dim_after * strata_weight) 
var_dim_after <- sum(strata_var_after * strata_weight)

# dat$pscat[dat$outofrange==0] = as.numeric(cut(dat$ps[dat$outofrange==0], breaks=c(0,cuts,1), include.lowest=TRUE))
# dat$pscat = as.factor(dat$pscat)
# pstab = with(dat, table(a,pscat))
# pstab = rbind(pstab, with(dat, table(pscat)))
# pstab = rbind(pstab, strata_dim)
# pstab = rbind(pstab, strata_var)
# pstab = rbind(pstab, strata_N1)
# pstab = rbind(pstab, strata_N0)
print("Logistic Before and after adjusting for covariates")
#print(pstab)

res <- matrix(c(strata_N0, strata_N1, strata_N1 + strata_N0, strata_dim, strata_var, strata_dim_after, strata_var_after), ncol= 4,byrow=TRUE)
colnames(res) <- c("1", "2", "3", "4")
rownames(res) <- c("0","1","total", "DIM Before Adjusting", "Var Before adjusting", "DIM After Adjusting", "Var after adjusting")
res <- as.table(res)
res

cat("DIM estimate", round(tau_dim, 5), "\n")
cat("Variance estimate", round(var_dim,5), "\n")
cat("DIM estimate After", round(tau_dim_after, 5), "\n")
cat("Variance estimate After", round(var_dim_after,5), "\n")
 #strata_N1
```

## For Random forest
```{r, echo = FALSE}
dat$outofrange[dat$ps>maxa0 & dat$a==1]=1
dat$outofrange[dat$ps<mina1 & dat$a==0]=1

dat$outofrangerf= rep(0, length(dat$outofrange))
# dat$outofrangerf[dat$psrf>maxa0 & dat$a==1]=1
# dat$outofrangerf[dat$psrf<mina1 & dat$a==0]=1
dat$outofrangerf = dat$outofrange
##### Define PS categories ##################
cuts = quantile(dat$psrf[dat$outofrangerf==0], seq(.25, .75, .25))
#dat$psrfcat[dat$outofrangerf==0] = as.numeric(cut(dat$psrf[dat$outofrangerf==0], breaks=c(0,cuts,1), include.lowest=TRUE))
#dat$psrfcat = as.factor(dat$psrfcat)
perc_list = cuts

strata_dim <- rep(0,length(perc_list)+1) 
strata_var <- rep(0,length(perc_list)+1) 
strata_weight <- rep(0,length(perc_list)+1)
strata_N1 <- rep(0,length(perc_list)+1) 
strata_N0 <- rep(0,length(perc_list)+1)

strata_dim_after <- rep(0,length(perc_list)+1) 
strata_var_after <- rep(0,length(perc_list)+1) 
strata_weight_after <- rep(0,length(perc_list)+1)

for(i in 1:(length(perc_list)+1))
{
  if (i ==1)
  {
    zst_ind <- which(dat$psrf >= 0 & dat$psrf <= perc_list[i] & dat$outofrangerf == 0)
    zst <- dat[dat$psrf >= 0 & dat$psrf <= perc_list[i] & dat$outofrangerf == 0, c("a", "pmfu")]
  } 
  else if( i == (length(perc_list)+1) )
  {
    zst_ind <- which(dat$psrf >= perc_list[i-1] & dat$psrf <= 1 & dat$outofrangerf == 0)
    zst <- dat[dat$psrf >= perc_list[i-1] & dat$psrf <= 1 & dat$outofrangerf == 0, c("a", "pmfu")]
  }
  else
  {
    #print("check")
    zst_ind <- which(dat$psrf >= perc_list[i-1] & dat$psrf <= perc_list[i] & dat$outofrangerf == 0)
    zst <- dat[dat$psrf >= perc_list[i-1] & dat$psrf <= perc_list[i] & dat$outofrangerf == 0, c("a", "pmfu")]
  }

  na_ind = which(is.na(zst[,"pmfu"]) == FALSE)
  zst = zst[na_ind,]
  N_1 <- sum(zst[,"a"]) 
  strata_N1[i] = N_1
  N_0 <- nrow(zst) - N_1 
  strata_N0[i] = N_0
  Z <- zst[,"a"]
  y <- zst[,"pmfu"]

  # Z = Z[na_ind]
  # y = y[na_ind]

  strata_dim[i] <- (1/N_1 * sum(Z * y) - 1/N_0 * sum((1 - Z) * y))
  V_1 <- compute_var(Z, N_1, y)
  V_0 <- compute_var(1-Z, N_0, y) 
  strata_var[i] <- V_1/N_1 + V_0/N_0
  strata_weight[i] <- nrow(zst)#/nrow(dat)

  lm_sub <- lm(pmfu ~ ., data = new_dat[zst_ind,], na.action = na.omit)
  strata_dim_after[i] <- lm_sub$coefficients[12]
  strata_var_after[i] <- (summary(lm_sub)$coefficients[12,2])^2
  strata_weight_after[i] <- length(zst)/length(which(dat$outofrange == 0))
}
strata_weight = strata_weight/sum(strata_weight)
tau_dim <- sum(strata_dim * strata_weight) 
var_dim <- sum(strata_var * strata_weight)

tau_dim_after <- sum(strata_dim_after * strata_weight) 
var_dim_after <- sum(strata_var_after * strata_weight)

# dat$pscat[dat$outofrange==0] = as.numeric(cut(dat$ps[dat$outofrange==0], breaks=c(0,cuts,1), include.lowest=TRUE))
# dat$pscat = as.factor(dat$pscat)
# pstab = with(dat, table(a,pscat))
# pstab = rbind(pstab, with(dat, table(pscat)))
# pstab = rbind(pstab, strata_dim)
# pstab = rbind(pstab, strata_var)
# pstab = rbind(pstab, strata_N1)
# pstab = rbind(pstab, strata_N0)
print("Random Forest before and after adjusting for covariates")
#print(pstab)

res <- matrix(c(strata_N0, strata_N1, strata_N1 + strata_N0, strata_dim, strata_var, strata_dim_after, strata_var_after), ncol= 4,byrow=TRUE)
colnames(res) <- c("1", "2", "3", "4")
#rownames(res) <- c("0","1","total", "DIM Before Adjusting", "Var Before adjusting", "DIM After Adjusting", "Var after adjusting")
res <- as.table(res)
res

cat("DIM estimate", round(tau_dim, 5), "\n")
cat("Variance estimate", round(var_dim,5), "\n")
cat("DIM estimate After", round(tau_dim_after, 5), "\n")
cat("Variance estimate After", round(var_dim_after,5), "\n")
 #strata_N1
```

```{r, echo = FALSE}
dat$outofrange[dat$psrf>maxa0 & dat$a==1]=1
dat$outofrange[dat$psrf<mina1 & dat$a==0]=1

##### Define PS categories ##################
cuts = quantile(dat$psrf[dat$outofrange==0], seq(.25, .75, .25)) # quartiles
dat$psrfcat[dat$outofrange==0] = as.numeric(cut(dat$psrf[dat$outofrange==0], breaks=c(0,cuts,1), include.lowest=TRUE))
dat$psrfcat = as.factor(dat$psrfcat)
perc_list = cuts

strata_dim <- rep(0,length(perc_list)+1) 
strata_var <- rep(0,length(perc_list)+1) 
strata_weight <- rep(0,length(perc_list)+1)

for (i in 1:(length(perc_list)+1))
{
  if (i ==1)
  {

    zst <- dat[dat$psrf >= 0 & dat$psrf <= perc_list[i] & dat$outofrange == 0, c("a", "pmfu")]
  } 
  else if( i == (length(perc_list)+1) )
  {
    zst <- dat[dat$psrf >= perc_list[i-1] & dat$psrf <= 1 & dat$outofrange == 0, c("a", "pmfu")]
  }
  else
  {
    #print("check")
    zst <- dat[dat$psrf >= perc_list[i-1] & dat$psrf <= perc_list[i] & dat$outofrange == 0, c("a", "pmfu")]
  }

  N_1 <- sum(zst[,"a"]) 
  #print(N_1)
  N_0 <- nrow(zst) - N_1 
  #print(N_0)
  Z <- zst[,"a"]
  y <- zst[,"pmfu"]
  na_ind = which(is.na(y) == FALSE)
  Z = Z[na_ind]
  y = y[na_ind]

  strata_dim[i] <- (1/N_1 * sum(Z * y) - 1/N_0 * sum((1 - Z) * y))
  V_1 <- compute_var(Z, N_1, y)
  V_0 <- compute_var(1-Z, N_0, y) 
  strata_var[i] <- V_1/N_1 + V_0/N_0
  strata_weight[i] <- nrow(zst) / nrow(dat) 
}
tau_dim <- sum(strata_dim * strata_weight) 
var_dim <- sum(strata_var * strata_weight)

dat$psrfcat[dat$outofrange==0] = as.numeric(cut(dat$psrf[dat$outofrange==0], breaks=c(0,cuts,1), include.lowest=TRUE))
dat$psrfcat = as.factor(dat$psrfcat)
psrftab = with(dat, table(a,psrfcat))
psrftab = rbind(psrftab, with(dat, table(psrfcat)))
psrftab = rbind(psrftab, strata_dim)
psrftab = rbind(psrftab, strata_var)
print("Random Forest without adjusting for covariates")
print(psrftab)

cat("DIM estimate", round(tau_dim, 5), "\n")
cat("Variance estimate", round(var_dim,5))
```

```{r, echo = FALSE}
dat$outofrange[dat$psrf>maxa0 & dat$a==1]=1
dat$outofrange[dat$psrf<mina1 & dat$a==0]=1
dat$ps = get_propensity_scores(method="logit")
dat$psrf = get_propensity_scores(method="RF")
dat$pslogit = get_propensity_scores(method="logit")

##### Define PS categories ##################
cuts = quantile(dat$psrf[dat$outofrange==0], seq(.25, .75, .25)) # quartiles
dat$psrfcat[dat$outofrange==0] = as.numeric(cut(dat$psrf[dat$outofrange==0], breaks=c(0,cuts,1), include.lowest=TRUE))
dat$psrfcat = as.factor(dat$psrfcat)
perc_list = cuts

strata_dim <- rep(0,length(perc_list)+1) 
strata_var <- rep(0,length(perc_list)+1) 
strata_weight <- rep(0,length(perc_list)+1)

for (i in 1:(length(perc_list)+1))
{
  if (i ==1)
  {
    zst <- which(dat$ps >= 0 & dat$ps <= perc_list[i] & dat$outofrange == 0)
  } 
  else if( i == (length(perc_list)+1) )
  {
    zst <- which(dat$ps >= perc_list[i-1] & dat$ps <= 1 & dat$outofrange == 0)
  }
  else
  {
    #print("check")
    zst <- which(dat$ps >= perc_list[i-1] & dat$ps <= perc_list[i] & dat$outofrange == 0)
  }

  # N_1 <- length(zst[,"a"]) 
  # print(N_1)
  # N_0 <- nrow(zst) - N_1 
  # print(N_0)
  # Z <- zst[,"a"]
  # y <- zst[,"mort_rate"]
  # na_ind = which(is.na(y) == FALSE)
  # #y[na_ind]
  # Z = Z[na_ind]
  # y = y[na_ind]

  lm_sub <- lm(pmfu ~ ., data = new_dat[zst,], na.action = na.omit)
  summary(lm_model1)

  strata_dim[i] <- lm_sub$coefficients[12]
  strata_var[i] <- (summary(lm_sub)$coefficients[12,2])^2
  strata_weight[i] <- length(zst)/length(which(dat$outofrange == 0))
}
tau_dim <- sum(strata_dim * strata_weight) 
var_dim <- sum(strata_var * strata_weight)

print("Logistic after adjusting for covariates")
dat$psrfcat[dat$outofrange==0] = as.numeric(cut(dat$psrf[dat$outofrange==0], breaks=c(0,cuts,1), include.lowest=TRUE))
dat$psrfcat = as.factor(dat$psrfcat)
psrftab = with(dat, table(a,psrfcat))
psrftab = rbind(psrftab, with(dat, table(psrfcat)))
psrftab = rbind(psrftab, strata_dim)
psrftab = rbind(psrftab, strata_var)
print(psrftab)

cat("DIM estimate", round(tau_dim, 5), "\n")
cat("Variance estimate", round(var_dim,5))
```

```{r, echo = FALSE}
dat$outofrange[dat$psrf>maxa0 & dat$a==1]=1
dat$outofrange[dat$psrf<mina1 & dat$a==0]=1
dat$ps = get_propensity_scores(method="logit")
dat$psrf = get_propensity_scores(method="RF")
dat$pslogit = get_propensity_scores(method="logit")

##### Define PS categories ##################
cuts = quantile(dat$psrf[dat$outofrange==0], seq(.25, .75, .25)) # quartiles
dat$psrfcat[dat$outofrange==0] = as.numeric(cut(dat$psrf[dat$outofrange==0], breaks=c(0,cuts,1), include.lowest=TRUE))
dat$psrfcat = as.factor(dat$psrfcat)
perc_list = cuts

strata_dim <- rep(0,length(perc_list)+1) 
strata_var <- rep(0,length(perc_list)+1) 
strata_weight <- rep(0,length(perc_list)+1)

for (i in 1:(length(perc_list)+1))
{
  if (i ==1)
  {
    zst <- which(dat$psrf >= 0 & dat$psrf <= perc_list[i] & dat$outofrange == 0)
  } 
  else if( i == (length(perc_list)+1) )
  {
    zst <- which(dat$psrf >= perc_list[i-1] & dat$psrf <= 1 & dat$outofrange == 0)
  }
  else
  {
    #print("check")
    zst <- which(dat$psrf >= perc_list[i-1] & dat$psrf <= perc_list[i] & dat$outofrange == 0)
  }

  # N_1 <- length(zst[,"a"]) 
  # print(N_1)
  # N_0 <- nrow(zst) - N_1 
  # print(N_0)
  # Z <- zst[,"a"]
  # y <- zst[,"mort_rate"]
  # na_ind = which(is.na(y) == FALSE)
  # #y[na_ind]
  # Z = Z[na_ind]
  # y = y[na_ind]

  lm_sub <- lm(pmfu ~ ., data = new_dat[zst,], na.action = na.omit)
  summary(lm_model1)

  strata_dim[i] <- lm_sub$coefficients[12]
  strata_var[i] <- (summary(lm_sub)$coefficients[12,2])^2
  strata_weight[i] <- length(zst)/length(which(dat$outofrange == 0))
}
tau_dim <- sum(strata_dim * strata_weight) 
var_dim <- sum(strata_var * strata_weight)

print("Random Forest after adjusting for covariates")
dat$psrfcat[dat$outofrange==0] = as.numeric(cut(dat$psrf[dat$outofrange==0], breaks=c(0,cuts,1), include.lowest=TRUE))
dat$psrfcat = as.factor(dat$psrfcat)
psrftab = with(dat, table(a,psrfcat))
psrftab = rbind(psrftab, with(dat, table(psrfcat)))
psrftab = rbind(psrftab, strata_dim)
psrftab = rbind(psrftab, strata_var)
print(psrftab)

cat("DIM estimate", round(tau_dim, 5), "\n")
cat("Variance estimate", round(var_dim,5))
```

@@
